---
title: "Creating a Wordle Game"
author: "Alexandra Boville"
date: "2024-02-12"
output: html_document
---

# Creating a Wordle Game

Loading libraries....
```{r}
library(tidyverse)
library(dplyr)

setwd("~/Desktop/BIO384K - Applied Data Analysis/Exercise 4/")
```


## Load Word Banks

1. List of official scrabble words based off of the Collins English Dictionary
2. List of 10,000 most common words in the English Language (no swear words)

```{r}
scrabble <- "/Users/allycat/Desktop/BIO384K - Applied Data Analysis/collins-scrabble-words-2019.txt"

common_words <- "/Users/allycat/Desktop/BIO384K - Applied Data Analysis/google-10000-english-usa-no-swears.txt"
```

Solution wordswill refer to common_words
valid words will refer to scrabble list

## Creating a Function that reads these data files

```{r}
load_dictionary <- function(filename) {
  read.delim(filename)
}

valid_list <- load_dictionary(scrabble)
str(valid_list)

solution_list <- load_dictionary(common_words)
str(solution_list)

```

## Reducing list of Solution Words that are only found in Valid Word list

```{r}
solution_list <- intersect(valid_list, solution_list)
solution_list
```

## Creating a Function that removes all words from Solution List that are not 5 letters in length, randomly choosing a word, and then splits the word into a vector of single-character elements

```{r}
pick_solution <- function(a) {
  a <- a$words
  a <- a[nchar(a)==5]
  a <- sample(a, 1)
  a <- str_split(a, "")
}

solution <- pick_solution(solution_list)
solution


```



```{r}
play_wordle <- function(solution, valid_list, num_guesses = 6) {
  print(paste("Let's Play Wordle! You have", num_guesses, "to guess a 5 letter word. Good Luck!")) #intro text to start game
  remaining_letters <- LETTERS #creating object for letters in alphabet
  guesses <- 0 #start count for number of guesses used so far
  
  while (guesses < num_guesses) { #while the attempts made is less than the limit for number of guesses... keep playing!
    print(paste(c("Remaining Letters:", remaining_letters), collapse = " ")) #print how many letters are left in the alphabet
    guesses <- guesses + 1 #increase the guess count by one
    guess_word <- readline(paste(" Enter your guess here: "))
    if (nchar(guess_word) != 5) { #checking that word entered has only 5 characters
      guess_word <- readline(paste0("Try another word! The word you guess must have 5 characters "))
    }
    guess_word <- toupper(guess_word) #ignoring case of word entered
    guess_word <- str_split(guess_word, "")
    
    round_result <- evaluate_guess(guess_word, solution) #evaluating guess
    remaining_letters <- setdiff(remaining_letters, guess_word)
    
    print(paste("Result: ", paste(rep("G", round_result$correct_guess), rep("Y", round_result$wrong_position), sep = ""), "\n"))
    
    if (round_result$correct_guess == 5) { #checking word and if it matches solution to print correct 
      print(paste("Congratulations! You guessed the word '", solution, "' and it is the correct answer! \n"))
      break
    }
    
    print(paste("Keep Trying! You have this many guesses left:", num_guesses - guesses, "\n"))
  }
  
  if (guesses == num_guesses) { #rprinting statemnet when you run out of guesses and lose game
    print(paste("Sorry, you ran out of guesses. The word was '", solution, "'. Better luck next time!\n"))
  }
}
``` 

## Write a Function to Evaluate entered guess words compared to the solution word
```{r}
evaluate_guess <- function(guess_word, solution) { 
  guess_vector <-str_split(guess_word, "") #splitting guessed word into vector of characters
  solution_vector <-str_split(solution, "") #splitting solution word into a vector of characters
  
  correct_guess <- sum(guess_vector == solution_vector) #determining if any letters guess are correct and if they are in right position
  wrong_position <- sum(guess_vector %in% solution_vector) - correct_guess
  
  return(list(correct_guess = correct_guess, wrong_position = wrong_position)) #returning letters that are correct and in correct position or correct but in wrong position
}
  
```

## Play Wordle!
```{r}
play_wordle(solution_list)
```

